Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
wrap text in table for better fit

tab_t %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = T)) %>%
  arrange(desc(Total)) %>%
  rename(Software = software_used) %>% 
  flextable() %>%
  autofit() %>%
  set_caption(
    "The frequency of use of top ten software programs by year of publication that were found to be used in the papers that were surveyed."
  )
```

>>>>

tab_t %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = T)) %>%
  arrange(desc(Total)) %>%
  rename(Software = software_used) %>% 
  flextable() %>%
  set_table_properties(layout = "autofit", width = 1) %>% 
  fontsize(size = 10) %>% 
  set_caption(
    "The frequency of use of top ten software programs by year of publication that were found to be used in the papers that were surveyed."
  )
```
